---
title: "MATH4753F25addisong"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{MATH4753F25addisong}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

```{r setup}
library(MATH4753F25addisong)
```

# 4 Working Functions

For each function, I just entered the function name into the R chunk to actually show what the function is and what the "insides" are. I also included a line of actually calling and running the function. I just used the example values from my roxygen skeleton to create these lines. I tried to use "?function_name" but the documentation would load in a separate screen (not the knitted HTML document), so I went with a different way to show off the function.

## birthday() Function

```{r}
birthday
birthday(10)
```

## mybin() Function

```{r}
mybin
mybin(iter=100,n=10,p=0.5)
```

## ntickets() Function

```{r}
ntickets
ntickets(N=400, gamma=0.02, p=0.95)
```

## myboot2() Function

```{r}
myboot2
set.seed(10); sam=rnorm(20,mean=10,sd=4)
myboot2(iter=10000,x=sam,fun="mean",alpha=0.05)
```

# 1 Data Set

```{r}
data("fire")
head(fire)
```
